Analysis and figures

### 2020-10-01 analysis/03_analysis.Rmd
Consistent figure colors and dimensions

```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(fastDummies)
library(scales)
library(patchwork)
library(ggstance)
library(here)

@@

```{r plot-total-giving, fig.width=4, fig.height=2.4}
ggplot(giving_aggregate, aes(x = Year, y = `Total donations`)) +
  geom_line(size = 1, color = clrs$maroon) +
  scale_x_continuous(breaks = seq(1980, 2015, 5)) +
  scale_y_continuous(labels = dollar, breaks = seq(100, 450, 50)) + 
  coord_cartesian(ylim = c(100, 450)) +
  labs(x = NULL, y = "Billions of dollars") + 
  theme_ngo(9)

@@

```{r plot-per-capita-giving, fig.width=6, fig.height=3.6}
ggplot(giving_per_capita, aes(x = Year, y = `Average giving`)) +
  geom_line(size = 1, color = clrs$green) +
  scale_x_continuous(breaks = seq(2000, 2014, 2)) +
  scale_y_continuous(labels = dollar, breaks = seq(1750, 2750, 250)) + 
  coord_cartesian(ylim = c(1750, 2750)) +
  labs(x = NULL, y = "Average annual donation") + 
  theme_ngo()

ggsave(here("analysis", "output", "figures", "giving_per_capita.pdf"), 
       width = 6, height = 3.6, units = "in", device = cairo_pdf)
ggsave(here("analysis", "output", "figures", "giving_per_capita.png"), 
       width = 6, height = 3.6, units = "in", type = "cairo", dpi = 300)
```

@@

```{r income-issue-funding-relationship, fig.width=6.5, fig.height=4.75}
plot_income_issue <- sim_clean %>% 
  group_by(org_issue, persona_income) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Issue area") %>% 
  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = fct_rev(persona_income))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002)),
                     breaks = seq(0, 0.06, 0.02)) +
  scale_color_manual(values = c(clrs$green, clrs$blue), guide = FALSE) +
  coord_cartesian(xlim = c(0, 0.06)) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_income_funding <- sim_clean %>% 
  group_by(org_funding, persona_income) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Funding sources") %>% 
  ggplot(aes(y = str_wrap(fct_rev(org_funding), 10), 
             x = avg_share, color = fct_rev(persona_income))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.06)) +
  scale_color_manual(values = c(clrs$green, clrs$blue), guide = FALSE) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_income_relationship <- sim_clean %>% 
  mutate(persona_income = fct_recode(persona_income,
                                     "< $61,372/year" = "Lower income",
                                     "> $61,372/year" = "Higher income")) %>% 
  group_by(org_relationship, persona_income) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Relationship with host government") %>% 
  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_income))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) +
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.003))) +
  coord_cartesian(xlim = c(0, 0.1)) +
  scale_color_manual(values = c(clrs$green, clrs$blue), 
                     guide = guide_legend(reverse = TRUE, nrow = 1)) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(str_wrap(facet, 50))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_income_relationship_extreme <- sim_excel_clean %>% 
  mutate(persona_income = fct_recode(persona_income,
                                     "$50,000/year" = "Lower income",
                                     "$100,000/year" = "Higher income"),
         org_relationship = fct_recode(org_relationship,
                                       "Under crackdown" = "Crackdown")) %>% 
  group_by(org_relationship, persona_income) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Relationship with host government") %>% 
  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_income))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.1)) +
  scale_color_manual(values = c(colorspace::darken(clrs$green, 0.4), 
                                colorspace::darken(clrs$blue, 0.6)), 
                     guide = guide_legend(reverse = TRUE, nrow = 1)) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(str_wrap(facet, 50))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_income <- plot_income_issue + plot_income_funding + 
  plot_income_relationship + plot_income_relationship_extreme +
  plot_layout(nrow = 2)

plot_income
ggsave(plot_income, filename = here("analysis", "output", "figures", "income-all.pdf"),
       width = 6.5, height = 4.75, units = "in", device = cairo_pdf)
ggsave(plot_income, filename = here("analysis", "output", "figures", "income-all.png"),
       width = 6.5, height = 4.75, units = "in", type = "cairo", dpi = 300)
```

@@

```{r edu-issue-funding-relationship, fig.width=5, fig.height=4.25}
plot_education_issue <- sim_clean %>% 
  group_by(org_issue, persona_education) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Issue area") %>% 
  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = fct_rev(persona_education))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.06)) +
  scale_color_manual(values = c(clrs$orange, clrs$purple), guide = FALSE) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_education_funding <- sim_clean %>% 
  group_by(org_funding, persona_education) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Funding sources") %>% 
  ggplot(aes(y = str_wrap(fct_rev(org_funding), 10), 
             x = avg_share, color = fct_rev(persona_education))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.06)) +
  scale_color_manual(values = c(clrs$orange, clrs$purple), guide = FALSE) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_education_relationship <- sim_clean %>% 
  group_by(org_relationship, persona_education) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Relationship with host government") %>% 
  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_education))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.1)) +
  scale_color_manual(values = c(clrs$orange, clrs$purple), 
                     guide = guide_legend(reverse = TRUE, ncol = 1)) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(str_wrap(facet, 20))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_education <- plot_education_issue + plot_education_funding + 
  plot_education_relationship + guide_area() + 
  plot_layout(guides = "collect", ncol = 2)
plot_education

ggsave(plot_education, filename = here("analysis", "output", "figures", "education-all.pdf"),
       width = 5, height = 4.25, units = "in", device = cairo_pdf)
ggsave(plot_education, filename = here("analysis", "output", "figures", "education-all.png"),
       width = 5, height = 4.25, units = "in", type = "cairo", dpi = 300)
```

@@

```{r religion-issue-funding-relationship, fig.width=5, fig.height=4.25}
plot_religion_issue <- sim_clean %>% 
  group_by(org_issue, persona_religion) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Issue area") %>% 
  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = fct_rev(persona_religion))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.06)) +
  scale_color_manual(values = c(clrs$red, clrs$navy), guide = FALSE) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_religion_funding <- sim_clean %>% 
  group_by(org_funding, persona_religion) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Funding sources") %>% 
  ggplot(aes(y = str_wrap(fct_rev(org_funding), 10), 
             x = avg_share, color = fct_rev(persona_religion))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.06)) +
  scale_color_manual(values = c(clrs$red, clrs$navy), guide = FALSE) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_religion_relationship <- sim_clean %>% 
  group_by(org_relationship, persona_religion) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Relationship with host government") %>% 
  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = fct_rev(persona_religion))) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.1)) +
  scale_color_manual(values = c(clrs$red, clrs$navy), 
                     guide = guide_legend(reverse = TRUE, ncol = 1)) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(str_wrap(facet, 20))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_religion <- plot_religion_issue + plot_religion_funding + 
  plot_religion_relationship + guide_area() + 
  plot_layout(guides = "collect", ncol = 2)
plot_religion

ggsave(plot_religion, filename = here("analysis", "output", "figures", "religion-all.pdf"),
       width = 5, height = 4.25, units = "in", device = cairo_pdf)
ggsave(plot_religion, filename = here("analysis", "output", "figures", "religion-all.png"),
       width = 5, height = 4.25, units = "in", type = "cairo", dpi = 300)
```

@@

```{r trust-issues}
plot_issue_social <- sim_clean %>% 
  group_by(org_issue, persona_trust, persona_ideology, persona_experience) %>% 
  summarize(avg_share = mean(share)) %>% 
  ggplot(aes(y = fct_rev(org_issue), x = avg_share, color = persona_trust)) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent) +
  scale_color_manual(values = c(clrs$orange, clrs$navy), guide = guide_legend(reverse = TRUE)) +
  labs(x = "Average share of donations", y = NULL, color = NULL) +
  facet_grid(rows = vars(persona_ideology), cols = vars(str_wrap(persona_experience, 100))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_issue_social
ggsave(plot_issue_social, filename = here("analysis", "output", "figures", "issue-social.pdf"),
       width = 6, height = 4.2, units = "in", device = cairo_pdf)
ggsave(plot_issue_social, filename = here("analysis", "output", "figures", "issue-social.png"),
       width = 6, height = 4.2, units = "in", type = "cairo", dpi = 300)
```

@@

```{r trust-relationship}
plot_relationship_social <- sim_clean %>% 
  group_by(org_relationship, persona_trust, persona_ideology, persona_experience) %>% 
  summarize(avg_share = mean(share)) %>% 
  ggplot(aes(y = fct_rev(org_relationship), x = avg_share, color = persona_trust)) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent) +
  scale_color_manual(values = c(clrs$orange, clrs$navy), guide = guide_legend(reverse = TRUE)) +
  labs(x = "Average share of donations", y = NULL, color = NULL) +
  facet_grid(rows = vars(persona_ideology), cols = vars(str_wrap(persona_experience, 100))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_relationship_social
ggsave(plot_relationship_social, filename = here("analysis", "output", "figures", "relationship-social.pdf"),
       width = 6, height = 4.2, units = "in", device = cairo_pdf)
ggsave(plot_relationship_social, filename = here("analysis", "output", "figures", "relationship-social.png"),
       width = 6, height = 4.2, units = "in", type = "cairo", dpi = 300)
```

@@

```{r trust-funding}
plot_funding_social <- sim_clean %>% 
  group_by(org_funding, persona_trust, persona_ideology, persona_experience) %>% 
  summarize(avg_share = mean(share)) %>% 
  ggplot(aes(y = str_wrap(fct_rev(org_funding), 20), x = avg_share, color = persona_trust)) +
  geom_pointrangeh(aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent) +
  scale_color_manual(values = c(clrs$orange, clrs$navy), guide = guide_legend(reverse = TRUE)) +
  labs(x = "Average share of donations", y = NULL, color = NULL) +
  facet_grid(rows = vars(persona_ideology), cols = vars(str_wrap(persona_experience, 100))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_funding_social
ggsave(plot_funding_social, filename = here("analysis", "output", "figures", "funding-social.pdf"),
       width = 6, height = 4.2, units = "in", device = cairo_pdf)
ggsave(plot_funding_social, filename = here("analysis", "output", "figures", "funding-social.png"),
       width = 6, height = 4.2, units = "in", type = "cairo", dpi = 300)
```

>>>>

```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(scales)
library(patchwork)
library(ggstance)
library(here)

# Wrap factor levels
# via Hadley: https://github.com/tidyverse/stringr/issues/107#issuecomment-233723948
str_wrap_factor <- function(x, ...) {
  levels(x) <- str_wrap(levels(x), ...)
  x
}

@@

```{r plot-total-giving, fig.width=4, fig.height=2.4, out.width="80%"}
ggplot(giving_aggregate, aes(x = Year, y = `Total donations`)) +
  geom_line(size = 1, color = clrs_ngo$vi_blue_dark) +
  scale_x_continuous(breaks = seq(1980, 2015, 5)) +
  scale_y_continuous(labels = dollar, breaks = seq(100, 450, 50)) + 
  coord_cartesian(ylim = c(100, 450)) +
  labs(x = NULL, y = "Billions of dollars") + 
  theme_ngo()

@@

```{r plot-per-capita-giving, fig.width=4, fig.height=2.4, out.width="80%"}
ggplot(giving_per_capita, aes(x = Year, y = `Average giving`)) +
  geom_line(size = 1, color = clrs_ngo$vi_blue_dark) +
  scale_x_continuous(breaks = seq(2000, 2014, 2)) +
  scale_y_continuous(labels = dollar, breaks = seq(1750, 2750, 250)) + 
  coord_cartesian(ylim = c(1750, 2750)) +
  labs(x = NULL, y = "Average annual donation") + 
  theme_ngo()
```

@@

```{r income-issue-funding-relationship, fig.width=6, fig.height=4.5, out.width="100%"}
plot_income_issue <- sim_clean %>% 
  group_by(org_issue, persona_income) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Issue area") %>% 
  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)),
             x = avg_share, color = fct_rev(persona_income))) +
  geom_pointrangeh(size = 0.75, fatten = 1.5,
                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002)),
                     breaks = seq(0, 0.06, 0.02)) +
  scale_color_manual(values = c(clrs_ngo$vi_turquoise, clrs_ngo$vi_purple), guide = FALSE) +
  coord_cartesian(xlim = c(0, 0.06)) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_income_funding <- sim_clean %>% 
  group_by(org_funding, persona_income) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Funding sources") %>% 
  ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 10)), 
             x = avg_share, color = fct_rev(persona_income))) +
  geom_pointrangeh(size = 0.75, fatten = 1.5,
                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.06)) +
  scale_color_manual(values = c(clrs_ngo$vi_turquoise, clrs_ngo$vi_purple), guide = FALSE) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_income_relationship <- sim_clean %>% 
  mutate(persona_income = fct_recode(persona_income,
                                     "< $61,372/year" = "Lower income",
                                     "> $61,372/year" = "Higher income")) %>% 
  group_by(org_relationship, persona_income) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Relationship with host government") %>% 
  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
             x = avg_share, color = fct_rev(persona_income))) +
  geom_pointrangeh(size = 0.75, fatten = 1.5, 
                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) +
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.003))) +
  coord_cartesian(xlim = c(0, 0.1)) +
  scale_color_manual(values = c(clrs_ngo$vi_turquoise, clrs_ngo$vi_purple), 
                     guide = guide_legend(reverse = TRUE, nrow = 1,
                                          override.aes = list(size = 0.25))) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(str_wrap(facet, 50))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_income_relationship_extreme <- sim_excel_clean %>% 
  mutate(persona_income = fct_recode(persona_income,
                                     "$50,000/year" = "Lower income",
                                     "$100,000/year" = "Higher income"),
         org_relationship = fct_recode(org_relationship,
                                       "Under crackdown" = "Crackdown")) %>% 
  group_by(org_relationship, persona_income) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Relationship with host government") %>% 
  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
             x = avg_share, color = fct_rev(persona_income))) +
  geom_pointrangeh(size = 0.75, fatten = 1.5,
                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.1)) +
  scale_color_manual(values = c(clrs_ngo$pl_yellow, clrs_ngo$pl_purple_light), 
                     guide = guide_legend(reverse = TRUE, nrow = 1,
                                          override.aes = list(size = 0.25))) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(str_wrap(facet, 50))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_income <- ((plot_income_issue + labs(x = NULL)) + 
  (plot_income_funding + labs(x = NULL))) / 
  (plot_income_relationship + plot_income_relationship_extreme)

plot_income
ggsave(plot_income, filename = here("analysis", "output", "figures", "income-all.pdf"),
       width = 6, height = 4.5, units = "in", device = cairo_pdf)
ggsave(plot_income, filename = here("analysis", "output", "figures", "income-all.png"),
       width = 6, height = 4.5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r edu-issue-funding-relationship, fig.width=8, fig.height=2.75, out.width="100%"}
plot_education_issue <- sim_clean %>% 
  group_by(org_issue, persona_education) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Issue area") %>% 
  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)), 
             x = avg_share, color = fct_rev(persona_education))) +
  geom_pointrangeh(size = 0.75, fatten = 1.5,
                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.06)) +
  scale_color_manual(values = c(clrs_ngo$pl_purple_dark, clrs_ngo$pl_orange), guide = FALSE) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_education_funding <- sim_clean %>% 
  group_by(org_funding, persona_education) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Funding sources") %>% 
  ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 10)), 
             x = avg_share, color = fct_rev(persona_education))) +
  geom_pointrangeh(size = 0.75, fatten = 1.5,
                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.06)) +
  scale_color_manual(values = c(clrs_ngo$pl_purple_dark, clrs_ngo$pl_orange), guide = FALSE) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_education_relationship <- sim_clean %>% 
  group_by(org_relationship, persona_education) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Relationship with host government") %>% 
  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)),
             x = avg_share, color = fct_rev(persona_education))) +
  geom_pointrangeh(size = 0.75, fatten = 1.5,
                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.1)) +
  scale_color_manual(values = c(clrs_ngo$pl_purple_dark, clrs_ngo$pl_orange), 
                     guide = guide_legend(reverse = TRUE, ncol = 1,
                                          override.aes = list(size = 0.25)),
                     labels = label_wrap(15)) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(str_wrap(facet, 20))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_education <- plot_education_issue + plot_education_funding + 
  plot_education_relationship + guide_area() +
  plot_layout(guides = "collect", ncol = 4)
plot_education
```

@@

```{r religion-issue-funding-relationship, fig.width=8, fig.height=2.75, out.width="100%"}
plot_religion_issue <- sim_clean %>% 
  group_by(org_issue, persona_religion) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Issue area") %>% 
  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)), 
             x = avg_share, color = fct_rev(persona_religion))) +
  geom_pointrangeh(size = 0.75, fatten = 1.5, 
                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.06)) +
  scale_color_manual(values = c(clrs_ngo$vi_blue_light, clrs_ngo$vi_yellow), guide = FALSE) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_religion_funding <- sim_clean %>% 
  group_by(org_funding, persona_religion) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Funding sources") %>% 
  ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 10)), 
             x = avg_share, color = fct_rev(persona_religion))) +
  geom_pointrangeh(size = 0.75, fatten = 1.5,
                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.06)) +
  scale_color_manual(values = c(clrs_ngo$vi_blue_light, clrs_ngo$vi_yellow), guide = FALSE) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(facet)) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_religion_relationship <- sim_clean %>% 
  group_by(org_relationship, persona_religion) %>% 
  summarize(avg_share = mean(share)) %>% 
  mutate(facet = "Relationship with host government") %>% 
  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
             x = avg_share, color = fct_rev(persona_religion))) +
  geom_pointrangeh(size = 0.75, fatten = 1.5,
                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  coord_cartesian(xlim = c(0, 0.1)) +
  scale_color_manual(values = c(clrs_ngo$vi_blue_light, clrs_ngo$vi_yellow), 
                     guide = guide_legend(reverse = TRUE, ncol = 1,
                                          override.aes = list(size = 0.25)),
                     labels = label_wrap(20)) +
  labs(x = "Average donation share", y = NULL, color = NULL) +
  facet_wrap(vars(str_wrap(facet, 20))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_religion <- plot_religion_issue + plot_religion_funding + 
  plot_religion_relationship + guide_area() +
  plot_layout(guides = "collect", ncol = 4)
plot_religion
```

## Education and religion across issue area, funding, and relationship

```{r education-religion-issue-funding-relationship, fig.width=6, fig.height=4.5, out.width="100%"}
plot_education_religion <- (plot_education_issue + labs(x = NULL)) + 
  (plot_education_funding + labs(x = NULL)) + 
  (plot_education_relationship + labs(x = NULL)) + 
  guide_area() +
  plot_religion_issue + 
  plot_religion_funding + 
  plot_religion_relationship +
  plot_layout(guides = "collect", ncol = 4)

plot_education_religion
ggsave(plot_education_religion, 
       filename = here("analysis", "output", "figures", "education-religion-all.pdf"),
       width = 6.5, height = 4.5, units = "in", device = cairo_pdf)
ggsave(plot_education_religion, 
       filename = here("analysis", "output", "figures", "education-religion-all.png"),
       width = 6.5, height = 4.5, units = "in", type = "cairo", dpi = 300)
```

@@

```{r trust-issues, fig.width=6, fig.height=4, out.width="100%"}
plot_issue_social <- sim_clean %>% 
  group_by(org_issue, persona_trust, persona_ideology, persona_experience) %>% 
  summarize(avg_share = mean(share)) %>% 
  ggplot(aes(y = fct_rev(str_wrap_factor(org_issue, 15)), 
             x = avg_share, color = persona_trust)) +
  geom_pointrangeh(size = 0.75, fatten = 1.5, 
                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  scale_color_manual(values = c(clrs_ngo$pl_blue, clrs_ngo$pl_pink), 
                     guide = guide_legend(reverse = TRUE,
                                          override.aes = list(size = 0.25))) +
  labs(x = "Average share of donations", y = NULL, color = NULL) +
  facet_grid(rows = vars(persona_ideology), cols = vars(str_wrap(persona_experience, 100))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_issue_social
ggsave(plot_issue_social, filename = here("analysis", "output", "figures", "issue-social.pdf"),
       width = 6, height = 4, units = "in", device = cairo_pdf)
ggsave(plot_issue_social, filename = here("analysis", "output", "figures", "issue-social.png"),
       width = 6, height = 4, units = "in", type = "cairo", dpi = 300)
```

@@

```{r trust-relationship, fig.width=6, fig.height=4, out.width="100%"}
plot_relationship_social <- sim_clean %>% 
  group_by(org_relationship, persona_trust, persona_ideology, persona_experience) %>% 
  summarize(avg_share = mean(share)) %>% 
  ggplot(aes(y = fct_rev(str_wrap_factor(org_relationship, 10)), 
             x = avg_share, color = persona_trust)) +
  geom_pointrangeh(size = 0.75, fatten = 1.5,
                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  scale_color_manual(values = c(clrs_ngo$pl_blue, clrs_ngo$pl_pink), 
                     guide = guide_legend(reverse = TRUE,
                                          override.aes = list(size = 0.25))) +
  labs(x = "Average share of donations", y = NULL, color = NULL) +
  facet_grid(rows = vars(persona_ideology), cols = vars(str_wrap(persona_experience, 100))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_relationship_social
ggsave(plot_relationship_social, filename = here("analysis", "output", "figures", "relationship-social.pdf"),
       width = 6, height = 4, units = "in", device = cairo_pdf)
ggsave(plot_relationship_social, filename = here("analysis", "output", "figures", "relationship-social.png"),
       width = 6, height = 4, units = "in", type = "cairo", dpi = 300)
```

@@

```{r trust-funding, fig.width=6, fig.height=4, out.width="100%"}
plot_funding_social <- sim_clean %>% 
  group_by(org_funding, persona_trust, persona_ideology, persona_experience) %>% 
  summarize(avg_share = mean(share)) %>% 
  ggplot(aes(y = fct_rev(str_wrap_factor(org_funding, 15)), 
             x = avg_share, color = persona_trust)) +
  geom_pointrangeh(size = 0.75, fatten = 1.5,
                   aes(xmin = 0, xmax = ..x..), position = position_dodge(width = 0.5)) + 
  scale_x_continuous(labels = percent_format(accuracy = 1), expand = expansion(add = c(0, 0.002))) +
  scale_color_manual(values = c(clrs_ngo$pl_blue, clrs_ngo$pl_pink), 
                     guide = guide_legend(reverse = TRUE,
                                          override.aes = list(size = 0.25))) +
  labs(x = "Average share of donations", y = NULL, color = NULL) +
  facet_grid(rows = vars(persona_ideology), cols = vars(str_wrap(persona_experience, 100))) +
  theme_ngo() +
  theme(panel.grid.major.y = element_blank())

plot_funding_social
ggsave(plot_funding_social, filename = here("analysis", "output", "figures", "funding-social.pdf"),
       width = 6, height = 4, units = "in", device = cairo_pdf)
ggsave(plot_funding_social, filename = here("analysis", "output", "figures", "funding-social.png"),
       width = 6, height = 4, units = "in", type = "cairo", dpi = 300)
```
